---
title: "Accuracy-Gunnison-All with canopy"
author: "Aji John"
date: "10/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## plot the raster parallel
```{r , echo=FALSE}
#library(rgdal)
library(ClusterR)
library(rasterVis)
library(RColorBrewer)
library(sf)
library(tidyverse)
  
```
```{r}
#library(terra)
library(raster)
```



```{r}
start_time <- Sys.time()
  beginCluster()
```



## Stack the layers

You can also embed plots, for example:

```{r , echo=FALSE}
aso_co <- raster('data/dem_stackedco_demandfriendsnormalized_asov3.tiff')
pred_co <- raster('data/dem_stackedco_demandfriendsnormalized_predv3.tiff')
```


## Lets stack them
```{r , echo=FALSE}

# fails
xy_crop <- stack(aso_co,pred_co)

aso_prj <- projectRaster(aso_co,pred_co, method="ngb")
extent(aso_prj)
extent(pred_co)

# succeeds 
xy_stack <- stack(aso_prj,pred_co)



```



## plot the RGB


```{r , echo=FALSE}


entire_co <- ggplot(xy_stack)  +  ggpubr::theme_pubclean() +
  labs(fill="",x="Longitude",y="Latitude") +  theme(legend.position = "none",axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
```



Using ceramic
```{r , echo=FALSE}
library('ceramic')

data("wrld_simpl", package = "maptools")
#im <- cc_location(cbind( -107.1661, 38.81874 ), buffer = 1e5, ype = "mapbox.satellite")
e_sta <- raster::extent(xy_stack)
im <- cc_location(e_sta, buffer = 1e5, ype = "mapbox.satellite")

#> Preparing to download: 12 tiles at zoom = 6 from 
#> https://api.mapbox.com/v4/mapbox.light/
raster::plotRGB(im)
```

# put the background
```{r , echo=FALSE}
#library(ggspatial)


gplot(xy_stack[[1]]) + 
  geom_tile(aes(fill = value))  +
  viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  theme_bw()

```

extent(rprob

# ASO
```{r , echo=FALSE}



aso_all<- gplot(xy_stack[[1]]) + 
  geom_tile(aes(fill = value))  +
  viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  #theme_bw() +
  ggpubr::theme_pubclean() +
  labs(fill="",x="Longitude",y="Latitude") +  theme(legend.position = "none") 
```

#Prediction
```{r , echo=FALSE}



prediction_all <- gplot(xy_stack[[2]]) + 
  geom_tile(aes(fill = value))  +
  viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  #theme_bw() +
  ggpubr::theme_pubclean() +
  labs(fill="",x="Longitude",y="Latitude") +  theme(legend.position = "none") 
```
Area 

```{r }
ggRGB(im, r=1,g=2, b=3)  +  ggpubr::theme_pubclean() +
  labs(fill="",x="Longitude",y="Latitude") +  theme(legend.position = "none",axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) 
area_sample <- ggRGB(im, r=1,g=2, b=3)  +  ggpubr::theme_pubclean() +
  labs(fill="",x="Longitude",y="Latitude") +  theme(legend.position = "none",axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) 
```

```{r }
#(combined_sites | (p2) | (world)) + plot_layout(guides = 'collect')
library(patchwork)
layout <- "
AAAA
AAAA
BBCC
BBCC
"
area_sample + aso_sample + prediction_sample +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = 'A', title = 'Sample Planet scene',
  subtitle = '',
  caption = 'Mosaic by Mapbox')
ggsave("figs/samplearea.png",dpi=300, dev='png',  height=10, width=10,units="in")
```
Redo the plots with Planet
planet+sample

```{r }
#(combined_sites | (p2) | (world)) + plot_layout(guides = 'collect')
library(patchwork)
layout <- "
AAAA
AAAA
BBBB
CCCC
"
planet_sample + aso_sample + prediction_sample +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = 'A', title = 'Sample Planet scene',
  subtitle = '',
  caption = 'Panel A copyrighted material of Planet Labs, Inc. All Rights Reserved.')
ggsave("figs/samplearea_planet.png",dpi=300, dev='png',  height=20, width=15,units="in",limitsize = FALSE)
```
Resample veg to match pred

```{r , echo=FALSE}

veg_vegResamp <- raster('data/Gunnison__chm_3p0m.tif')
newproj <- "+proj=longlat +datum=WGS84"
pr2 <- projectRaster(veg_vegResamp, crs=newproj,res=res(rpredasoclip))
writeRaster(pr2, 'data/Gunnison__chm_2point1by1point6.tif', overwrite=TRUE, options="COMPRESS=LZW") 
veg_crop<-crop(pr2,extent(rpredasoclip))


```

Stack the layers with pred and aso

So, two ways of doing it, first crop, or do or find the overlao and crop

```{r }


veg_all <- raster('data/Gunnison__chm_2point1by1point6.tif')

veg_crop_gunni<-crop(veg_all,extent(xy_stack))

 # calculate overlap between the two datasets
 overlap <- raster::intersect(extent(xy_stack), extent(veg_crop_gunni))
  veg_crop_gunni <- crop(veg_crop_gunni, overlap)
  xy_crop <-  crop(xy_stack, overlap)
  
extent(veg_crop_gunni) <- extent(xy_crop)
  
rpredasochmall <- stack(xy_crop,veg_crop_gunni)

data_matrix_withchm <- as.data.frame(rasterToPoints(rpredasochmall))
head(rpredasochmall)

colnames(data_matrix_withchm) <- c('longitude','latitude','aso','pred','canopyheight')

library(caret)
data_matrix_withchm_filtered <- data_matrix_withchm[complete.cases(data_matrix_withchm),]

confusionMatrix(as.factor(data_matrix_withchm_filtered$aso),as.factor(data_matrix_withchm_filtered$pred),mode = 'prec_recall')

```
Greater than 1m  (f-score)

```{r }
data_matrix_withchm_filtered_1 <- data_matrix_withchm_filtered  %>% filter(canopyheight > 1) %>% as.data.frame()

confusionMatrix(as.factor(data_matrix_withchm_filtered_1$aso),as.factor(data_matrix_withchm_filtered_1$pred),mode = 'prec_recall')

```

```{r }
#(combined_sites | (p2) | (world)) + plot_layout(guides = 'collect')
library(patchwork)
layout <- "
AAAA
AAAA
BBCC
BBCC
"
area_sample + aso_sample + prediction_sample +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = 'A', title = 'Sample Planet scene',
  subtitle = '',
  caption = 'Mosaic by Mapbox')
ggsave("figs/samplearea.png",dpi=300, dev='png',  height=10, width=10,units="in")
```

Plot along with vegetation metrucs

```{r , echo=FALSE}
data_matrix <- rasterToPoints(rpredasoclip)
head(data_matrix)
datafra_comb <- data_matrix %>% as.data.frame()
colnames(datafra_comb) <- c('longitude','latitude','aso','pred')

library(caret)
datafra_comb_filtered <- datafra_comb[complete.cases(datafra_comb),]

```


Get the points

```{r , echo=FALSE}
data_matrix <- rasterToPoints(rpredasoclip)
head(data_matrix)
datafra_comb <- data_matrix %>% as.data.frame()
colnames(datafra_comb) <- c('longitude','latitude','aso','pred')

library(caret)
datafra_comb_filtered <- datafra_comb[complete.cases(datafra_comb),]

```

```{r , echo=FALSE}
confusionMatrix(as.factor(datafra_comb_filtered$aso),as.factor(datafra_comb_filtered$pred),mode = 'prec_recall')
```


Accuracy assesment by only extracting the pixel values


# get values
```{r , echo=FALSE}

aso_df <- raster::extract(rpredasoclip[[1]], raster::extent(rpredasoclip))
pred_df <- raster::extract(rpredasoclip[[2]], raster::extent(rpredasoclip))

aso_df <- as.data.frame(aso_df)
pred_df <- as.data.frame(pred_df)

df <- data.frame(aso_df,pred_df)
colnames(df) <- c('aso','pred')
```

# Far more efficient, sum the layers
```{r , echo=FALSE}
library(caret)
df_filtered <- df[complete.cases(df),]
#confusionMatrix(df$aso,df$pred,mode = 'prec_recall')
```

```{r , echo=FALSE}
confusionMatrix(as.factor(df_filtered$aso),as.factor(df_filtered$pred),mode = 'prec_recall')
```

Lets add NDVI classification

```{r , echo=FALSE}

data_matrix_ndvi <- as.data.frame(rasterToPoints(planet_ndvi))
head(data_matrix_ndvi)
colnames(data_matrix_ndvi) <- c('longitude','latitude','ndvi')


```

left outer join

```{r , echo=FALSE}
library(dplyr)
matchasopredndvi <- datafra_comb_filtered %>% full_join(data_matrix_ndvi)

library(caret)
matchasopredndvi_filtered <- matchasopredndvi[complete.cases(matchasopredndvi),]
```

```{r , echo=FALSE}

gplot(im[[3]]) + 
  geom_tile(aes(fill = value))  +
  viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  theme_bw()

```


```{r , echo=FALSE}
endCluster()
end_time <- Sys.time()
end_time - start_time

```

```{r , echo=FALSE}
library(rgdal)
library(rasterVis)
library(RColorBrewer)

colr <- colorRampPalette(brewer.pal(2, 'RdYlBu'))

rpredasoclip <-  raster::stack('data/asopluspredclippedplanet.tiff')
rasterVis::levelplot(rpredasoclip, 
          margin=FALSE,                       # suppress marginal graphics
          colorkey=list(
            space='bottom',                   # plot legend at bottom
            labels=list(at=-5:5, font=4)      # legend ticks and labels 
          ),    
          par.settings=list(
            axis.line=list(col='transparent') # suppress axes and legend outline
          ),
          scales=list(draw=FALSE),            # suppress axis labels
          col.regions=colr,                   # colour ramp
          at=seq(-5, 5, len=101))


```
## visualize the planet tile
```{r , echo=FALSE}
vi2 <- function(x, y) {
    (x - y) / (x + y)
}
ndvi2gunni <- terra::lapp(planet_area_ref_wgs84[[4:3]], fun=vi2)
plot(ndvi2gunni, col=rev(terrain.colors(10)), main="Planet-NDVI Gunnison")

```


## Create shapefile for Gunnison (utility)
```{r , echo=FALSE}

e <- raster::extent(raster::raster(aso_co))
p <- as(e, 'SpatialPolygons')
crs(p) <-"+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
shapefile(p, 'data/gunnison.shp')
```

```{r , echo=FALSE}
library(sp)
library(sf)
#library(raster)
library(rosm)
library(ggspatial)
library(ggsn)

#ASO 
TV_dem <- raster::stack('data/asopluspredclippedplanet.tiff')[[1]]
tv_xmin <- extent(TV_dem)[1]
tv_xmax <- extent(TV_dem)[2]
tv_ymin <- extent(TV_dem)[3]
tv_ymax <- extent(TV_dem)[4]

ggspatial::ggplot(x = extent(tv_xmin, tv_xmax + 0.0275, tv_ymin, tv_ymax), 
           type = 'cartolight') +
  annotation_map_tile(zoomin = -1) +
    annotation_spatial(TV_dem, aes(fill = band1), alpha = 0.5) + 
  # C:\OSGeo4W64\apps\qgis-ltr\resources\cpt-city-qgis-min\bhw\bhw2\bhw2_39.svg:
  scale_fill_gradientn(colours=c('#28dce2', '#8f5dd5', '#8f5dd5' ,'#ffff80', 
                                 '#f4893a', '#994469', '#581389' ),
                                values = c(0.0000, 0.1299, 0.2600, 0.4800, 
                                           0.5901, 0.7900, 1.000)) +
  ggsn::north(x.min = tv_xmin, x.max = tv_xmax + 0.0235,
              y.min = tv_ymin, y.max = tv_ymin - 0.001, 
              symbol = 7, scale = 0.08) +
  ggsn::scalebar(x.min = tv_xmin, x.max = tv_xmax, 
                 y.min = tv_ymin, y.max = tv_ymax,
                 anchor = c(x = tv_xmax + 0.025, y = tv_ymin),
                 height = 0.015, dist = 1, st.size = 3, 
                 dd2km = TRUE, model = 'WGS84') +
  ggtitle('SRTM DEM-S Elevation', subtitle = 'Townsville 1:25,000 topographic key map sheet') + 
  labs(x = 'Longitude', y = 'Latitude', fill = 'Elevation (m)') +
  guides(fill = guide_colorbar(override.aes = list(alpha = 0.5))) +
  theme(legend.position = c(0.9, 0.5),
        legend.background = element_rect(fill = alpha('white', 0)),
        legend.key.height = unit(0.7, "in")) +
  coord_fixed()

```

# get values
```{r , echo=FALSE}

aso_df <- terra::values(aso_co,mat=FALSE)
pred_df <- terra::values(predclip_co,mat=FALSE)

aso_df <- as.data.frame(aso_df)
pred_df <- as.data.frame(pred_df)

df <- data.frame(aso_df,pred_df)
colnames(df) <= c('aso','pred')
```


# Far more efficient, sum the layers
```{r , echo=FALSE}
library(caret)
df_filtered <- df[complete.cases(df),]
#confusionMatrix(df$aso,df$pred,mode = 'prec_recall')
```

```{r , echo=FALSE}
confusionMatrix(as.factor(df_filtered$aso),as.factor(df_filtered$pred),mode = 'prec_recall')
```

# Far more efficient, sum the layers
```{r , echo=FALSE}
s <- app(x, fun=sum,nodes=8)
```

# plot the added raster - 0 - good, 1- disagee , 2- agree
```{r , echo=FALSE}
plot(s)
```


```{r , echo=FALSE}
nosnowmatch <- freq(s, value=0)
nosnowmismatch <- freq(s, value=1)
snowsnowmatch <- freq(s, value=2)

total_matchmismatch <- nosnowmatch[3] + nosnowmismatch[3] + snowsnowmatch[3]
```


leaflet
```{r , echo=FALSE}
library(leaflet)
agreeordis <- raster(s)
m <- leaflet() %>% setView(lng = -107, lat = 38.9, zoom = 15)
m %>% 
  addProviderTiles("Esri.WorldImagery") 
```


# utterly inefocent code
```{r , echo=FALSE}
#data_matrix_co <- as.points(x)
#head(data_matrix_co)
```



Do the complete plot
```{r, echo=FALSE}

gunniasoandpred <- raster::stack('data/asopluspredclippedplanet.tiff')
```


```{r , echo=FALSE}
# Area calc

raster::area(projectRaster(gunniasoandpred[[2]], crs = "+init=epsg:32631"))
# All area 733.5
# class      : RasterLayer 
#dimensions : 461, 662, 305182  (nrow, ncol, ncell)
#resolution : 22.5, 32.6  (x, y)
#extent     : 1029602, 1044497, 5178034, 5193063  (xmin, xmax, ymin, ymax)
#crs        : +proj=utm +zone=31 +datum=WGS84 +units=m +no_defs 
#source     : memory
#names      : layer 
#values     : 733.5, 733.5  (min, max)
#This is in Km2

```



```{r , echo=FALSE}
library('ceramic')
aoi_study_area <- raster::stack('data/newstudy-co-large.tif')

whole_area_co <- raster('./data/dem_stackedco_demandfriendsnormalized_asov3.tiff')

data("wrld_simpl", package = "maptools")
#im <- cc_location(cbind( -107.1661, 38.81874 ), buffer = 1e5, ype = "mapbox.satellite")

im_gunni_site <- cc_location(extent(aso_co), buffer = 1e5, ype = "mapbox.satellite")
#im <- cc_location(p, ype = "mapbox.terrain-rgb")

#raster::writeRaster(im_gunni_site,'data/Gunni-whole.tiff',overwrite=TRUE)
#raster::writeRaster(im_swiss_site,'data/swiss-_aoi.tiff',overwrite=TRUE)

# then do
# gdalwarp  -t_srs EPSG:4326 Gunni-whole.tif Gunni-whole_wgs84.tif

#> Preparing to download: 12 tiles at zoom = 6 from 
#> https://api.mapbox.com/v4/mapbox.light/
raster::plotRGB(im_gunni_site)
#writeRaster(raster(im_gunni_site),filename = './data/whole_area_gunnison_tiff',overwrite=TRUE)
```



```{r , echo=FALSE}

aoi_large_gunni <-raster::stack('data/newstudy-gunni-large_aoi_wgs84.tif')



#poly_study_gunni <- as(aoi_large_gunni,'SpatialPolygons')

#poly_study_gunni <- fortify(poly_study_gunni)


aoi_gunni_co <- extent(aoi_large_gunni)
poly_aoi_gunni_co<- as(aoi_gunni_co,'SpatialPolygons')

p_study_gunni <- fortify(poly_aoi_gunni_co)

```

```{r , echo=FALSE}
#aoi_Gunni <- raster::stack('./data/Gunni-aoi_wgs84.tif')

whole_area_co <- raster::stack('./data/Gunni-whole_wgs84.tif')

plotgc <- RStoolbox::ggRGB(whole_area_co)+
    coord_sf(crs = 4326)+
theme(panel.background = element_rect(colour = "black", fill="white"),
      axis.text.x = element_text(angle = 45, hjust = 1)) +
#ggspatial::annotation_scale(  pad_x = unit(0.5, "mm"),pad_y = unit(0.5, "mm"),location = "bl", width_hint = 0.5) +
#   ggspatial::annotation_north_arrow(location = "tr", which_north = "true", 
#       pad_x = unit(0.5, "mm"),pad_y = unit(0.5, "mm"),style = #ggspatial::north_arrow_fancy_orienteering) +
 geom_polygon(aes(long,lat), alpha = 0.2, color='green',data = p_study_gunni) +
#coord_equal() +
  labs(x='',  y='') 

```

```{r, echo=FALSE}
# Vector of correspondence
cols.nb <- c("0" = "blue", "1" = "red")
library(patchwork)
plotga <- gplot(aso_co) + 
  geom_tile(aes(fill = as.character(value)) ) +
   coord_sf(crs = 4326)+
  scale_fill_manual(values = cols.nb,
                    breaks = 0:1,
                    labels = c("No snow", "Snow"),
                    name = "") +
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "bottom",
      axis.text.x = element_text(angle = 45, hjust = 1)) +
ggspatial::annotation_scale(location = "br", width_hint = 0.2) +
    ggspatial::annotation_north_arrow(location = "tr", which_north = "true", 
       #pad_y = unit(0.2, "mm"),
       style = ggspatial::north_arrow_fancy_orienteering,
       height = unit(0.8, "cm"),
  width = unit(0.5, "cm")) +
    geom_polygon(aes(long,lat), alpha = 0.2, color='green',data = p_study_gunni) +
  theme(legend.position = "none") +
   theme(axis.text.y=element_blank()) +
  labs(x='',  y='') 


plotgb <- gplot(pred_co) + 
  geom_tile(aes(fill = as.character(value)) ) +
   coord_sf(crs = 4326)+
  scale_fill_manual(values = cols.nb,
                    breaks = 0:1,
                    labels = c("No snow", "Snow"),
                    name = "") +
  #theme_bw()+
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "none",
      axis.text.x = element_text(angle = 45, hjust = 1)) +
#ggspatial::annotation_scale(location = "tr", width_hint = 0.2) +
#    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
#       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
    geom_polygon(aes(long,lat), alpha = 0.2, color='green',data = p_study_gunni) +
  theme(legend.position = "none") +
     theme(axis.text.y=element_blank()) +
  labs(x='',  y='') 

# Area calc

#raster::area(projectRaster(aoi_SWiss[[1]], crs = "+init=epsg:32631"))
# All area 733.5
# class      : RasterLayer 
#dimensions : 461, 662, 305182  (nrow, ncol, ncell)
#resolution : 22.5, 32.6  (x, y)
#extent     : 1029602, 1044497, 5178034, 5193063  (xmin, xmax, ymin, ymax)
#crs        : +proj=utm +zone=31 +datum=WGS84 +units=m +no_defs 
#source     : memory
#names      : layer 
#values     : 733.5, 733.5  (min, max)
#This is in Km2

```


Area of the study
```{r , echo=FALSE}
library(patchwork)
layout <- "
ABC
"
 plotgc + plotgb + plotga  +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = 'A', title = '',
  subtitle = '',
  caption = 'Mapbox (C)') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("figs/gunnison_all_ms.png",dpi=300, dev='png',  height=6, width=10,units="in")
```


```{r , echo=FALSE}
endCluster()
end_time <- Sys.time()
end_time - start_time

```