---
title: "Accuracy-CO- Entire prediction"
author: "Aji John"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r }
library(raster)
```

## Plot the stuff 

ASO
```{r pressure, echo=FALSE}
aso<- raster('data/dem_stackedco_demandfriendsnormalized_asov3.tiff')
pred <- raster('data/dem_stackedco_demandfriendsnormalized_predv3.tiff')

plot(aso)
```

Prediction

```{r , echo=FALSE}

plot(pred)
```
Stacking fails because of extent mimatch

```{r , echo=FALSE}
extent(aso)
extent(pred)
df <- stack(aso,pred)
```
>class      : RasterLayer 
dimensions : 23037, 20992, 483592704  (nrow, ncol, ncell)
resolution : 2.145767e-05, 1.670038e-05  (x, y)
extent     : -107.2156, -106.7651, 38.71124, 39.09596  (xmin, xmax, ymin, ymax)
crs        : +proj=utm +zone=13 +datum=WGS84 +units=m +no_defs 
source     : /Users/ajijohn/git/planet-snowcove-R/data/dem_stackedco_demandfriendsnormalized_asov3.tiff 
names      : dem_stackedco_demandfriendsnormalized_asov3 
values     : -32768, 32767  (min, max)

> 
> pred
class      : RasterLayer 
dimensions : 23038, 20992, 483613696  (nrow, ncol, ncell)
resolution : 2.145767e-05, 1.670017e-05  (x, y)
extent     : -107.2156, -106.7651, 38.71122, 39.09596  (xmin, xmax, ymin, ymax)
crs        : +proj=utm +zone=13 +datum=WGS84 +units=m +no_defs 
source     : /Users/ajijohn/git/planet-snowcove-R/data/dem_stackedco_demandfriendsnormalized_predv3.tiff 
names      : dem_stackedco_demandfriendsnormalized_predv3 
values     : -32768, 32767  (min, max)



```{r , echo=FALSE}
aso_prj <- projectRaster(aso,pred)
extent(aso_prj)
extent(pred)
writeRaster(aso_prj, filename="data/dem_stackedco_demandfriendsnormalized_asov3_reprg.tiff", format="GTiff", overwrite=TRUE)
```


```{r , echo=FALSE}
df <- stack(aso_prj,pred)
plot(aso_prj)
```

```{r , echo=FALSE}
data_matrix <- rasterToPoints(df)
head(data_matrix)

```

```{r , echo=FALSE}
library(tidyverse)
datafra_comb <- data_matrix %>% as.data.frame()
```

```{r , echo=FALSE}
library(tidyverse)

datafra_comb %>%summarise_all(~ sum(is.na(.)))
```
No effect on dropping of NAs
```{r , echo=FALSE}
datafra_comb_dropna <- datafra_comb %>% filter_all(any_vars(!is.na(.))) %>% as.data.frame()

#datafra_comb_dropna %>% filter(demnormalized_stacked_predv3 < 0) %>% tally()
```
Remove NAs

```{r , echo=FALSE}
datafra_comb_fixed <- datafra_comb_dropna[complete.cases(datafra_comb_dropna),]

```
Not used now

```{r , echo=FALSE}
#vals_pred <- getValues(pred)
#vals_aso <- getValues(aso_prj)

```

```{r , echo=FALSE}
datafra_comb_dropna_mod <- datafra_comb_dropna

```


```{r , echo=FALSE}
library(caret)
colnames(datafra_comb_fixed) <- c('longitude','latitude','aso','pred')

datafra_comb_fixed$aso <- round(datafra_comb_fixed$aso)
perf<- confusionMatrix(as.factor(datafra_comb_fixed$aso), as.factor(datafra_comb_fixed$pred),mode = "prec_recall")
```

```{r , echo=FALSE}
perf

```

```{r , echo=FALSE}
class <- c("Accuracy", "Precision","Recall","F-score","Balanced Accuracy","Kappa")
metrics<- c(0.8995,0.9456 ,0.9273 , 0.9364, 0.8585 ,0.6971   )
library(tidyverse)
perf<- data.frame(class, metrics)
colnames(perf) <- c('class','f_score')
perf %>% ggplot() + geom_bar(aes(class,metrics),stat="identity") +
 labs(x="Scores" , y="Metrics",subtitle="Gunnison basin performance") + theme_minimal(base_size = 12)+
  ggpubr::theme_pubclean()
ggsave(filename = "figs/allpreditCO.png",dpi = 300,height=4,width=8,units="in")
```

stack vegetation, need to do some stuff 

```{r , echo=FALSE}
veg_all <- raster('data/Gunnison__chm_2point1by1point6.tif')
# calculate overlap between the two datasets
overlap <- raster::intersect(extent(df), extent(veg_all))
veg_crop_allpred <- crop(veg_all, overlap)

# extents are still diff , res is slightly diff too

crs(veg_crop_allpred) <- crs(df)
extent(veg_crop_allpred) <- extent(df)

allpredwithveg <- stack(df,veg_crop_allpred)
```

       