---
title: "R Notebook CH Results"
output: html_notebook
---

## R Markdown

Read the layer
```{r}
library(raster)

```

get the area

```{r , echo=FALSE}
library('ceramic')
aoi <- extent(c(10.02339, 10.04452, 46.5633, 46.58303 ))
p <- aoi
data("wrld_simpl", package = "maptools")
#im <- cc_location(cbind( -107.1661, 38.81874 ), buffer = 1e5, ype = "mapbox.satellite")

im <- cc_location(p, buffer = 1e5, ype = "mapbox.satellite")
#im <- cc_location(p, ype = "mapbox.terrain-rgb")

#raster::writeRaster(im,'data/newstudy-swiss-large_aoi.tiff',overwrite=TRUE)

#> Preparing to download: 12 tiles at zoom = 6 from 
#> https://api.mapbox.com/v4/mapbox.light/
raster::plotRGB(im)
```

Load aoi and plot
```{r}

aoi_large_SWiss <-raster::stack('data/newstudy-swiss-large_aoi_wgs84.tif')
plotRGB(aoi_large_SWiss)
```
Area of the snipped region
```{r}

raster::area(projectRaster(aoi_large_SWiss[[1]], crs = "+init=epsg:32631"))
```


class      : RasterLayer 
dimensions : 615, 696, 428040  (nrow, ncol, ncell)
resolution : 2.67, 3.87  (x, y)
extent     : 1038000, 1039858, 5180628, 5183008  (xmin, xmax, ymin, ymax)
crs        : +proj=utm +zone=31 +datum=WGS84 +units=m +no_defs 
source     : memory
names      : layer 
values     : 10.3329, 10.3329  (min, max)


```{r}
combined_CH_Raster_lage_SWiss <-raster::stack('data/newstudy-swiss-large.tif')
```

CHM
```{r}
plot(combined_CH_Raster_lage_SWiss[[3]])
```


Read the DCE
```{r}
combined_CH_Raster_lage_SWiss_dce <-raster::stack('data/newstudywithdce-swiss-large.tif')[[3]]
plot(combined_CH_Raster_lage_SWiss_dce)
```
With canopy density
```{r}
combined_CH_Raster_lage_SWiss_cd <-raster::stack('data/newstudywithcd-swiss-large.tif')[[3]]
plot(combined_CH_Raster_lage_SWiss_cd)
```

created open and forested area map

```{r}
moafa <- c(-10, 1, 0,  1, 100, 1)
rclmatoafa <- matrix(moafa, ncol=1, byrow=TRUE)
r_chmoafa <- reclassify(combined_CH_Raster_lage_SWiss[[3]], rclmatoafa)


plot(r_chmoafa)
```

```{r setup, include=FALSE}
library(ForestGapR)
library(fieldRS)
library(viridis)
library(rasterVis)
library(tidyverse)
```

create the plots

```{r}
cols.nb <- c("0" = "blue", "1" = "red")
plotb2 <- gplot(combined_CH_Raster_lage_SWiss[[2]]) + 
  geom_tile(aes(fill = as.character(value)) ) +
   coord_sf(crs = 4326)+
  scale_fill_manual(values = cols.nb,
                    breaks = 0:1,
                    labels = c("No snow", "Snow"),
                    name = "") +
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "none",
       axis.text.x = element_text(angle = 45, hjust = 1)) +
ggspatial::annotation_scale(location = "tr", width_hint = 0.2) +
    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
  labs(x='',  y='') 


plotb1 <- gplot(combined_CH_Raster_lage_SWiss[[1]]) + 
  geom_tile(aes(fill = as.character(value)) ) +
   coord_sf(crs = 4326)+
  scale_fill_manual(values = cols.nb,
                    breaks = 0:1,
                    labels = c("No snow", "Snow"),
                    name = "") +
  #theme_bw()+
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "none",
       axis.text.x = element_text(angle = 45, hjust = 1)) +
ggspatial::annotation_scale(location = "tr", width_hint = 0.2) +
    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
  labs(x='',  y='') 

 
plota1 <-  RStoolbox::ggRGB(im)+
theme(panel.background = element_rect(colour = "black", fill="white")) +
ggspatial::annotation_scale(location = "bl", width_hint = 0.5) +
    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
  labs(x='',  y='') 
```


get Plabet imagery

```{r, echo=FALSE}
planet_img_swiss_stack <-raster::stack('data/20170516_092458_1030_3B_AnalyticMS_SR_clip_wgs84.tif')
#planet_img_swiss_stack <- planet_img_swiss_stack/10000
plotc3 <-  RStoolbox::ggRGB(planet_img_swiss_stack)+
theme(panel.background = element_rect(colour = "black", fill="white")) +
  labs(x='',  y='') 
```

```{r, echo=FALSE}
planet_crop <- crop(planet_img_swiss_stack,p)
plotb3 <-  RStoolbox::ggRGB(planet_crop)+
   coord_sf(crs = 4326)+
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "bottom",
       axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x='',  y='') 
```


```{r , echo=FALSE}

cols.dc <- c("1" = "red", "2" = "blue", "3" = "green")
rc_density_ms<- reclassify(combined_CH_Raster_lage_SWiss_cd, c(-Inf,0.5,1,0.5,0.75,2, 0.75,1,3))

plota1<- gplot(rc_density_ms) + 
  geom_tile(aes(fill = as.character(value)) ) +
   coord_sf(crs = 4326)+
  scale_fill_manual(values = cols.dc,
                    breaks = c(1,2,3),
                    labels = c("Sparse", "Medium","Dense"),
                    name = "") +
  #theme_bw()+
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "bottom",
       axis.text.x = element_text(angle = 45, hjust = 1)) +
ggspatial::annotation_scale(location = "tr", width_hint = 0.2) +
    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
  labs(x='',  y='',fill="Vegetation:",color="Vegetation:") 



cols.chm <- c("1" = "red", "2" = "green")
#old
#rc_dce <- reclassify(df_dce[[3]], c(-Inf,0,1,0,30,2, 30,Inf,3))
#new
rc_chm_ms<- reclassify(combined_CH_Raster_lage_SWiss[[3]], c(-Inf,1,1,1,Inf,2))

plota2<- gplot(rc_chm_ms) + 
  geom_tile(aes(fill = as.character(value)) ) +
   coord_sf(crs = 4326)+
  scale_fill_manual(values = cols.chm,
                    breaks = c(1,2),
                    labels = c("Open", "Forested"),
                    name = "") +
  #theme_bw()+
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "bottom",
       axis.text.x = element_text(angle = 45, hjust = 1)) +
ggspatial::annotation_scale(location = "tr", width_hint = 0.2) +
    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
  labs(x='',  y='',fill="Vegetation:",color="Vegetation:") 


cols.dce <- c("1" = "green", "2" = "blue", "3" = "red")
#old
#rc_dce <- reclassify(df_dce[[3]], c(-Inf,0,1,0,30,2, 30,Inf,3))
#new
rc_dce_ms <- reclassify(combined_CH_Raster_lage_SWiss_dce, c(-Inf,0,1,0,30,2, 30,Inf,3))

plota3<- gplot(rc_dce_ms) + 
  geom_tile(aes(fill = as.character(value)) ) +
   coord_sf(crs = 4326)+
  scale_fill_manual(values = cols.dce,
                    breaks = c(1,2,3),
                    labels = c("Dense", "Medium","Sparse"),
                    name = "") +
  #theme_bw()+
theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "bottom",
      axis.text.x = element_text(angle = 45, hjust = 1)) +
ggspatial::annotation_scale(location = "tr", width_hint = 0.2) +
    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
  labs(x='',  y='',fill="Vegetation:",color="Vegetation:") 

```

Prepare C - Area, chm and dem

```{r, echo=FALSE}
asodem_img_swiss_stack <-raster::stack('data/EUCHDB20170829f1a1_DEM_wgs84.tiff')
#planet_img_swiss_stack <- planet_img_swiss_stack/10000

```

```{r, echo=FALSE}
aso_swiss_dem_crop <- crop(asodem_img_swiss_stack,p)
plotc3 <-  gplot(aso_swiss_dem_crop)+
   coord_sf(crs = 4326)+
  geom_tile(aes(fill = value))  +
 viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "bottom",
      axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x='',  y='', fill="DEM (m)") 
```

```{r , echo=FALSE}



plotc1 <- RStoolbox::ggRGB(aoi_large_SWiss)+
    coord_sf(crs = 4326)+
theme(panel.background = element_rect(colour = "black", fill="white"),axis.text.x = element_text(angle = 45, hjust = 1)) +
ggspatial::annotation_scale(location = "bl", width_hint = 0.5) +
    ggspatial::annotation_north_arrow(location = "bl", which_north = "true", 
       pad_y = unit(0.2, "mm"),style = ggspatial::north_arrow_fancy_orienteering) +
  labs(x='',  y='') 

plotc2 <- gplot(combined_CH_Raster_lage_SWiss[[3]]) +
    coord_sf(crs = 4326)+
  geom_tile(aes(fill = value))  +
 viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  theme(panel.background = element_rect(colour = "black", fill="white"),legend.position = "bottom",
      axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x='',  y='', fill="Canopy height (m)") 
  
```



```{r , echo=FALSE}
library(patchwork)
layout <- "
ABC
DEF
"
 plotb1 + plotb2 + plotb3  +
  plota1+plota2+plota3+
  plot_layout(design = layout) +
  plot_annotation(tag_levels = 'A', title = '',
  subtitle = '',
  caption = 'Planet (C)') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("figs/swiss_aoi_ms.png",dpi=300, dev='png',  height=8, width=12,units="in")
```


Area of the study
```{r , echo=FALSE}
library(patchwork)
layout <- "
ABC
"
 plotc1 + plotc2 + plotc3  +
  plot_layout(design = layout) +
  plot_annotation(tag_levels = 'A', title = '',
  subtitle = '',
  caption = 'Mapbox (C)') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggsave("figs/swiss_aoi_data_ms.png",dpi=300, dev='png',  height=8, width=12,units="in")
```


Lets do complete study Area
