---
title: "extract values-raster"
author: "Aji John"
date: "11/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(exactextractr)
library(terra)
```

## R Markdown

Extracts the values of cells in a Raster* that are covered by a simple feature collection containing polygonal geometries, as well as the fraction of each cell that is covered by the polygon. Returns either the result of a summary operation or function applied to the values and coverage fractions (if fun is specified), or a data frame containing the values and coverage fractions themselves (if fun is NULL.)


```{r cars}
rast <- raster::raster(matrix(1:100, ncol=10), xmn=0, ymn=0, xmx=10, ymx=10)
poly <- sf::st_as_sfc('POLYGON ((2 2, 7 6, 4 9, 2 2))')

# named summary operation on RasterLayer, returns vector
exact_extract(rast, poly, 'mean')
#> [1] 43.16667

# two named summary operations on RasterLayer, returns data frame
exact_extract(rast, poly, c('min', 'max'))
#>   min max
#> 1  25  65

# named summary operation on RasterStack, returns data frame
stk <- raster::stack(list(a=rast, b=sqrt(rast)))
exact_extract(stk, poly, 'mean')
#>     mean.a   mean.b
#> 1 43.16667 6.525083

# named weighted summary operation, returns vector
weights <- raster::raster(matrix(runif(100), ncol=10), xmn=0, ymn=0, xmx=10, ymx=10)
exact_extract(rast, poly, 'weighted_mean', weights=weights)
#> [1] 43.34777

# custom summary function, returns vector
exact_extract(rast, poly, function(value, cov_frac) length(value[cov_frac > 0.9]))
#> [1] 7
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
