---
title: "ForestDynamics"
author: "Aji John"
date: "12/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r }
library(ForestGapR)
library(fieldRS)
library(viridis)
```

```{r , echo=FALSE}
k.img <- unsuperClass(planet_ndvi, nSamples=5000, nClasses=5)$map
plot(k.img)
```
```{r , echo=FALSE}
ndvi.max <- calc(planet_ndvi, fun=max) # derive maximum NDVI composite)
seg.img <- ccLabel(ndvi.max, method="spatial", change.threshold=5)$regions # segment NDVI image
```


```{r , echo=FALSE}
seg.img <- pixFilter(seg.img, 10, "erode")
```


Finally, we will use extractFields() to derive polygons for each segment. This function will draw a polygon based on the extent of each segment. This can be useful when dealing with noisy images as the ones used in this example. However, as the plot below shows, the output might still require some manual editing.

```{r , echo=FALSE}
fields <- extractFields(seg.img, method="complex")
```


## Including Plots

You can also embed plots, for example:

```{r , echo=FALSE}
# Plotting chm
#plot(veg_crop, col=viridis(10))
 
# Setting height thresholds (e.g. 10 meters)
threshold<-2
size<-c(1,100) # m2

# Detecting forest gaps
gaps_duc<-getForestGaps(chm_layer=veg_crop, threshold=threshold, size=size)

# Plotting gaps
plot(gaps_duc, col="red", add=TRUE, main="Forest Canopy Gap", legend=FALSE)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
