---
title: "analyze-stuff"
author: "Aji John"
date: "2/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Read the layer
```{r}
library(raster)

```

## Including Plots

You can also embed plots, for example:
class      : Extent 
xmin       : 578434.7 
xmax       : 580026.2 
ymin       : 5157167 
ymax       : 5159338 


```{r pressure, echo=FALSE}
newExtent <- extent(c(578434.7,580026.2 ,5157167 ,5159338 ))

library(sp)


e <- as(newExtent, "SpatialPolygons")
sp::proj4string(e) <- proj4string(planet_img_swiss)
e.geo <- sp::spTransform(e, CRS("+proj=longlat +datum=WGS84 +no_defs 
                             +ellps=WGS84 +towgs84=0,0,0"))
  
aoi <- extent(c(10.02339, 10.04452, 46.5633, 46.58303 ))
p <- aoi
```

```{r}
library(rgdal)

#darat_rg <- readGDAL('./data/study-area-predicted.tiff')
#creates a hige file - Skipping
#writeOGR(darat_rg, layer="band1","data/studyarea.geojson",driver="GeoJSON")

```

```{r}
library(sp)
enew <- as(raster::extent(10.02339, 10.04452, 46.5633, 46.58303), "SpatialPolygons")
proj4string(enew) <- "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"
plot(enew)
library(geojson)
asgeojs <- as.geojson(enew)

geo_pretty(asgeojs)

```

{
    "type": "FeatureCollection",
    "features": [
        {
            "type": "Feature",
            "id": 0,
            "properties": {
                "dummy": 0.0
            },
            "geometry": {
                "type": "Polygon",
                "coordinates": [
                    [
                        [
                            10.0201,
                            46.5818
                        ],
                        [
                            10.0201,
                            46.5887
                        ],
                        [
                            10.03,
                            46.5887
                        ],
                        [
                            10.03,
                            46.5818
                        ],
                        [
                            10.0201,
                            46.5818
                        ]
                    ]
                ]
            }
        }
    ]
}
 


=======


#visualize
```{r , echo=FALSE}
library('ceramic')

data("wrld_simpl", package = "maptools")
#im <- cc_location(cbind( -107.1661, 38.81874 ), buffer = 1e5, ype = "mapbox.satellite")

aoip<- cc_location(aoi, buffer = 1e5, ype = "mapbox.satellite")
#im <- cc_location(p, ype = "mapbox.terrain-rgb")

#> Preparing to download: 12 tiles at zoom = 6 from 
#> https://api.mapbox.com/v4/mapbox.light/
raster::plotRGB(aoip)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

Plot the area of interest (Bounding box)

class      : Extent 
xmin       : 10.02011 
xmax       : 10.03 
ymin       : 46.58182 
ymax       : 46.58873 


Using ceramic
```{r , echo=FALSE}
library('ceramic')

data("wrld_simpl", package = "maptools")
#im <- cc_location(cbind( -107.1661, 38.81874 ), buffer = 1e5, ype = "mapbox.satellite")

im <- cc_location(p, buffer = 1e5, ype = "mapbox.satellite")
#im <- cc_location(p, ype = "mapbox.terrain-rgb")

#> Preparing to download: 12 tiles at zoom = 6 from 
#> https://api.mapbox.com/v4/mapbox.light/
raster::plotRGB(im)
```

# Clip the prediction

```{r pressure, echo=FALSE}
library(rgdal)
pred<- raster('data/pred_merged_UTM_3m_s1_nodata_ch_r1.tif')
crs_latlong <-crs("+proj=longlat +datum=WGS84")

pred_ref_wgs84 <- projectRaster(pred,crs=crs_latlong,method='ngb')

#pred <- raster('data/dem_stackedco_demandfriendsnormalized_predv3.tiff')
pred_crop <- crop(pred_ref_wgs84,p)
plot(pred_crop)
```



# Clip the ASO

```{r pressure, echo=FALSE}

aso<- raster('data/EUCHDB20170517_SUPERsnow_depth_3m_binary_wgs84_3m.tif')
#crs_latlong <-crs("+proj=longlat +datum=WGS84")

#pred_ref_wgs84 <- projectRaster(pred,crs=crs_latlong)

#pred <- raster('data/dem_stackedco_demandfriendsnormalized_predv3.tiff')
aso_crop <- crop(aso,p)
plot(aso_crop)
```

Clip the canopy

```{r , echo=FALSE}

chm<- raster('data/EUCHDB20170829f1a1_CHM_WGS84.tif')
#crs_latlong <-crs("+proj=longlat +datum=WGS84")

#chm_ref_wgs84 <- projectRaster(chm,crs=crs_latlong)

#pred <- raster('data/dem_stackedco_demandfriendsnormalized_predv3.tiff')
chm_crop <- crop(chm,p)
plot(chm_crop)
```


```{r , echo=FALSE}

aso_pred_rep <- projectRaster(aso_crop,pred_crop,method='ngb')
chm_crop_rep <- projectRaster(chm_crop,pred_crop)
extent(aso_pred_rep) <- extent(pred_crop)
extent(chm_crop_rep) <- extent(pred_crop)
df <- stack(aso_pred_rep,pred_crop,chm_crop_rep)

raster::writeRaster(df,'data/newstudy-swiss-large.tiff',overwrite=TRUE)
```


```{r , echo=FALSE}

data_matrix <- rasterToPoints(df)
head(data_matrix)
datafra_comb <- data_matrix %>% as.data.frame()

colnames(datafra_comb) <- c('x','y','aso','pred','veg_height')
```

```{r , echo=FALSE}
library(caret)
datafra_comb1m <- datafra_comb %>% dplyr::filter(!is.na(veg_height) & veg_height > 2) %>% as.data.frame()

high_veg <- datafra_comb1m %>% dplyr::filter(!is.na(veg_height)) %>% dplyr::filter(veg_height > 1 ) %>% as.data.frame()
high_veg_df <- high_veg %>% dplyr::mutate(pred_f = as.factor(pred),aso_f = as.factor(aso)) %>% as.data.frame()

confusionMatrix(as.factor(high_veg$aso),as.factor(high_veg$pred),mode = 'prec_recall')

```

```{r , echo=FALSE}
library(caret)

low_veg <- datafra_comb %>%  dplyr::filter(veg_height < 2 ) %>% as.data.frame()
low_veg_df <- low_veg %>% dplyr::mutate(pred_f = as.factor(pred),aso_f = as.factor(aso)) %>% as.data.frame()

confusionMatrix(as.factor(low_veg$aso),as.factor(low_veg$pred),mode = 'prec_recall')

```

```{r , echo=FALSE}
library(caret)

bare_veg <- datafra_comb %>%  dplyr::filter(veg_height < 1 ) %>% as.data.frame()
bare_veg_df <- bare_veg %>% dplyr::mutate(pred_f = as.factor(pred),aso_f = as.factor(aso)) %>% as.data.frame()

confusionMatrix(as.factor(bare_veg$aso),as.factor(bare_veg$pred),mode = 'prec_recall')

```





```{r , echo=FALSE}
lin <- function(x){x * 10 + 0.6}

# TPI for different neighborhood size:
tpiw <- function(x, w=5) {
	m <- matrix(1/(w^2-1), nc=w, nr=w)
	m[ceiling(0.5 * length(m))] <- 0
	f <- focal(x, m)
	x - f
}

cd <- function(x, w) {
	m <- matrix(1, nc=w, nr=w)
#	m[ceiling(0.5 * length(m))] <- 0
	f <- focal(x, m, fun=sum)
	f
}

```


```{r , echo=FALSE}
library(tidyverse)
library(rasterVis)
# 225m2
#canden5by5wc <- cd(split_chm1, w=5)
canden3by3wc <- cd(chm_crop, w=3)

rcwc <- reclassify(canden3by3wc, c(0, 50, 100,150, 200, 250))

gplot(rcwc) + 
  geom_tile(aes(fill = value))  +
 viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  theme_bw()

#ggsave(filename = "figs/wc_densitymap.png",dpi = 300,height=4,width=8,units="in")
```
## Reclassify the canopy height layer

```{r , echo=FALSE}

m <- c(-10, 2, 0,  2, 100, 1)
rclmat <- matrix(m, ncol=3, byrow=TRUE)
r_chm <- reclassify(chm_crop, rclmat)

cdensity <- function(x, w) {
	m <- matrix(1, nc=w, nr=w)
#	m[ceiling(0.5 * length(m))] <- 0
	f <- focal(x, m, fun=mean)
	f
}

# 225m2
#canden5by5wc <- cd(split_chm1, w=5)
c_density3by3wc <- cdensity(r_chm, w=3)


gplot(c_density3by3wc) + 
  geom_tile(aes(fill = value))  +
 viridis::scale_fill_viridis(direction = -1, na.value='#FFFFFF00') + 
  theme_bw()

ggsave(filename = "figs/densitymap.png",dpi = 300,height=4,width=8,units="in")
```
Add Density
```{r , echo=FALSE}
aso_crop_reprcd <- projectRaster(aso_crop,c_density3by3wc,method='ngb')
pred_crop_reprcd <- projectRaster(pred_crop,c_density3by3wc,method='ngb')

extent(aso_crop_reprcd)  <- extent(c_density3by3wc)
df_cd <- stack(aso_crop_reprcd,pred_crop_reprcd,c_density3by3wc)

raster::writeRaster(df_cd,'data/newstudywithcd-swiss-large.tiff',overwrite=TRUE)
```

```{r , echo=FALSE}

data_matrix_cd <- rasterToPoints(df_cd)
head(data_matrix_cd)
datafra_comb_cd <- data_matrix_cd %>% as.data.frame()

colnames(datafra_comb_cd) <- c('x','y','aso','pred','can_den')
```

```{r , echo=FALSE}
library(caret)
datafra_comb1m_cd <- datafra_comb_cd %>% dplyr::filter(!is.na(can_den) & can_den > .75) %>% as.data.frame()

dense_veg <- datafra_comb1m_cd %>% dplyr::filter(!is.na(can_den)) %>% dplyr::filter(can_den > .75 ) %>% as.data.frame()
dense_veg_df <- dense_veg %>% dplyr::mutate(pred_f = as.factor(pred),aso_f = as.factor(aso)) %>% as.data.frame()

confusionMatrix(as.factor(dense_veg$aso),as.factor(dense_veg$pred),mode = 'prec_recall')

```

```{r , echo=FALSE}
library(caret)
datafra_comb1m_cd <- datafra_comb_cd %>% dplyr::filter(!is.na(can_den) & can_den > .5 & can_den < .75) %>% as.data.frame()

dense_veg <- datafra_comb1m_cd %>% dplyr::filter(!is.na(can_den)) %>% dplyr::filter(  can_den > .5 & can_den < .75 ) %>% as.data.frame()


confusionMatrix(as.factor(dense_veg$aso),as.factor(dense_veg$pred),mode = 'prec_recall')

```

```{r , echo=FALSE}
library(caret)
datafra_comb1m_cd <- datafra_comb_cd %>% dplyr::filter(!is.na(can_den) & can_den < .5) %>% as.data.frame()

dense_veg <- datafra_comb1m_cd %>% dplyr::filter(!is.na(can_den)) %>% dplyr::filter(can_den < .5 ) %>% as.data.frame()

confusionMatrix(as.factor(dense_veg$aso),as.factor(dense_veg$pred),mode = 'prec_recall')

```


Look at DCe

```{r , echo=FALSE}
planet_img_swiss <-raster('data/20170516_092458_1030_3B_AnalyticMS_SR_clip.tif')
dce_met <- raster('./data/dce_Swiss9_out.asc')
projection(dce_met) <- projection(planet_img_swiss)

dce_ref_wgs84 <- projectRaster(dce_met,crs=crs_latlong,method='ngb')
cropped_dce <- crop(dce_ref_wgs84, p)

aso_crop_reprdce <- projectRaster(aso_crop,cropped_dce,method='ngb')
pred_crop_reprdce<- projectRaster(pred_crop,cropped_dce,method='ngb')


df_dce <- stack(aso_crop_reprdce,pred_crop_reprdce,cropped_dce)

raster::writeRaster(df_dce,'data/newstudywithdce-swiss-large.tiff',overwrite=TRUE)
```

Plot the DCE Metrics

```{r , echo=FALSE}

data_matrix_dce <- rasterToPoints(df_dce)
head(data_matrix_dce)
datafra_comb_dce <- data_matrix_dce %>% as.data.frame()

colnames(datafra_comb_dce) <- c('x','y','aso','pred','dce')
datafra_comb_orig <- datafra_comb_dce
```

```{r , echo=FALSE}
library(caret)
datafra_comb_dce <- datafra_comb_orig %>% dplyr::filter(!is.na(dce) & dce <0) %>% as.data.frame()

dense_dce<- datafra_comb_dce %>% dplyr::filter(!is.na(dce)) %>% dplyr::filter(dce < 0 ) %>% as.data.frame()


confusionMatrix(as.factor(dense_dce$aso),as.factor(dense_dce$pred),mode = 'prec_recall')

```


```{r , echo=FALSE}
library(caret)
datafra_comb_dce <- datafra_comb_orig %>% dplyr::filter(!is.na(dce) & dce >0  & dce < 30) %>% as.data.frame()

med_dce<- datafra_comb_dce %>% dplyr::filter(!is.na(dce)) %>% dplyr::filter(dce >0  & dce < 30) %>% as.data.frame()


confusionMatrix(as.factor(med_dce$aso),as.factor(med_dce$pred),mode = 'prec_recall')

```

```{r , echo=FALSE}
library(caret)
datafra_comb_dce <- datafra_comb_orig %>% dplyr::filter(!is.na(dce) & dce > 30) %>% as.data.frame()

low_dce<- datafra_comb_dce %>% dplyr::filter(!is.na(dce)) %>% dplyr::filter( dce > 30) %>% as.data.frame()


confusionMatrix(as.factor(low_dce$aso),as.factor(low_dce$pred),mode = 'prec_recall')

```
