---
title: "R Notebook"
output: html_notebook
---


```{r}
# second step: apply the function
library(raster)
gunni_layers <- raster::brick('./data/gunnison_dem3m_rep4326.tiff')

gunni_dem <- tuol_layers[[1]]

```


```{r}
# TPI for different neighborhood size:
# first step: define customized function
tpiw <- function(x, w=5) {
    m <- matrix(1/(w^2-1), nc=w, nr=w)
    m[ceiling(0.5 * length(m))] <- 0
    f <- focal(x, m)
    x - f
}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
# second step: apply the function
gunni_25 <- tpiw(gunni_dem, w=25)
gunni_25
```



Stacj


```{r}
# second step: apply the function
gunni_layers_tpi <- stack(gunni_dem,gunni_25)
gunni_layers_tpi

writeRaster(gunni_layers_tpi, 'data/gunnison_dem3m_rep4326_withtpi.tif', overwrite=TRUE, options="COMPRESS=LZW") 
```